\chapter{Linear Algebra}
\section{Matrix}
Rectangular array of numbers:
$$
    \begin{bmatrix}
        1 & 2 & 3 \\
        4 & 5 & 6 \\
    \end{bmatrix}
$$

\paragraph*{Dimension of the matrix:} \#rows x \#cols (2 x 3)

\paragraph*{Elements of the matrix:}
\begin{align*}
    A      & =	\begin{bmatrix}
        1 & 2 & 3 \\
        4 & 5 & 6 \\
    \end{bmatrix}                                 \\
    A_{ij} & = \text{``$i,j$ entry'' in the $i^{th}$ row, $j^{th}$ col} \\
\end{align*}

\section{Vector}
An $n \times 1$ matrix.
\begin{align*}
    y & =	\begin{bmatrix}
        1 \\
        2 \\
        3 \\
        4 \\
    \end{bmatrix} \\
    y_i = i^{th} \text{ element}   \\
\end{align*}

\paragraph*{Note:} Uppercase for matrices, lowercase for vectors.

\section{Addition and Scalar Multiplication}
Add/Subtract (element by element) matrices of same dimention only!

Multiply/Divide (all elements) a matrix by scalar!

\section{Matrix Matrix Multiplication}
$m \times n$ matrix multiplied by $n \times o$ matrix gives a $m \times o$ matrix.

\subsection*{Properties}
\begin{enumerate}
    \item Matrix Multiplication is \emph{not} Commutative.
    \item Matrix Multiplication is Associative.
    \item \emph{Identity Matrix ($I$):} $1$'s along diagonal, $0$'s everywhere else in an
          $n \times n$ matrix. $AI = IA = A$.
\end{enumerate}

\section{Inverse and Transpose}

\subsection*{Inverse}
Only square ($n \times n$) matrices \emph{may} have an inverse.

$$AA^{-1} = A^{-1}A = I$$.

Matrices that don't have an inverse	are \emph{singular} or \emph{degenerate} matrices.

\subsection*{Transpose}
Let $A$ be an $m \times n$ matrix and let $B = A^T$, then
$$ B_{ij} = A_{ji} $$
Example:
\begin{align*}
    A       & =	\begin{bmatrix}
        1 & 2 & 3 \\
        4 & 5 & 6 \\
    \end{bmatrix} \\
    B = A^T & =	\begin{bmatrix}
        1 & 4 \\
        2 & 5 \\
        3 & 6 \\
    \end{bmatrix} \\
\end{align*}

% \blfootnote{Check \autoref{lecture3} for more details.}
\blfootnote{Check \href{lecture_pdf/Lecture3.pdf}{Lecture3.pdf} for more details.}
